Malacology: A Programmable Storage System

### 2016-10-20 paper/paper.tex
update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>
paper: finish mantle evaluation
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We wanted to implement CORFU and we had two choices: build it from the ground
up or do it on top of Malacology. To show the feasability of building on
Malacology our evaluation focuses on the performance of the internal
abstractions when used to construct the Mantle and ZLog services. First, we
benchmark scenarios where contention is at the sequencer by examining the
interfaces used to map ZLog onto Malacology; specifically, we describe the
sequencer implementation and the propagation of object \& data interfaces
interfaces. Next, we benchmark scenarios when there are multiple logs by using
Mantle to (1) balance sequencers across a cluster and (2) recover from failure.

@@

We have conducted our evaluation on CloudLab as well as our own 20 node
cluster. We follow the ``Popper Convention"~\cite{anonymous} so as to try and
make our experiments as reproducible as possible. We have a GitHub repository
with our source code, experimental environment, configuration parameters, and
workloads but due to the double-blind policy, we have temporarily disabled the
links to our graphs and experimental details.

@@

While a best-effort approach to sharing capabilities makes sense for a file
system client, throughput drops significantly with two clients as the majority
of the time neither client has the capability as it ping-pongs between
clients. This observation reveals a tuning parameter: how long a client
maintains its capability lease. In throughput labeled $2C,<time>$ we show
aggregate throughput as we decrease the amount of time that a client holds its
lease before responding to a request for the capability.  At lease times as
low as 10ms throughput achieve a significant proportion of the locally cached
throughput.

@@

\subsection{Load Balancing Multiple ZLog Sequencers with Mantle}

For scenarios with multiple shared logs and many clients, co-locating
sequencers on the same physical node is not ideal. Unfortunately, building a
load balancer that can migrate the shared resource (in this case, the resource
that guards the current token) would require building subsystems for migrating
resources, monitoring the workloads, monitoring physical nodes, partitioning
resources, cache roherence, and managing multiple sequencers.

The following experiments demonstrate the feasibility of using the mechanisms
of the Malacology load balancing interface (e.g., migrating, monitoring, and
partitioning load) to (1) alleviate load from overloaded servers with multiple
sequencers and (2) recover from failure.

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-balancer-behaviors.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}] The
load balancing interface alleviates overloaded servers in environments with multiple sequencers in
}\label{fig:mantle-balancer-behaviors}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-balancer-performance.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}]
}\label{fig:mantle-balancer-performance}
\end{figure}

The experiments are run on a cluster with 10 nodes to store objects, one node
to monitor the cluster, and 3 nodes that can accomodate sequencers. Our first
experiment co-locates 3 sequencers each with 4 clients on the same physical
server.  Instead of measuring contention at the clients like we did in
Section~\ref{sec:sequencer-implementation}, these experiments create contention
at the sequencers by setting the capability infrastructure to ``round trip
mode". In this mode clients go to the sequencer for every request. We
implement this by piggybacking on \texttt{fstat()} and using the shared
resource interface to force round trips.  Because the sequencer hands out
positions for the tail of the log, the workload is read-heavy.

Figure~\ref{fig:mantle-balancer-behaviors} shows the throughput (\(y\) axis)
over time (\(x\) axis) of different load balancers that migrate ZLog sequencers
acround the cluster; ``No Balancing" keeps all sequencers on one server,
``CephFS" migrates sequencers using the original algorithms packaged with Ceph,
and the ``Mantle" curve shows the throughput of a custom load balancer we wrote
specifically for sequencers. The increased throughput for the ``CephFS" and
``Mantle" curves between 0 and 60 seconds are a result of migrating the
sequencer(s) off of overloadeed servers. In addition to showing that migrating
sequencers improves performance, Figure~\ref{fig:mantle-balancer-behaviors}
also demonstrates features that we will explore in the rest of this section.
Section~\ref{sec:feature-balancing-modes} and~\ref{sec:feature-migration-units}
shows why the performance of Mantle is better than CephFS when the cluster
stabilizes at time 100 seconds and Section~\ref{sec:feature-backoff} explains
the slope and location of the rebalancing phase between 0 and 60 seconds by
comparing the aggressiveness of the CephFS and Mantle balancers.

@@

The load balancing service can operate in different balancing modes that stress
the subsystems that handle client requests or forwarded requests in different
ways. In Figure~\ref{fig:mantle-balancer-behaviors}, the ``CephFS" curve shows
the performance of the balancing mode that CephFS uses {\it most of the time}.
CephFS has 3 modes for balancing load: CPU mode, workload mode, and hybrid
mode. All three have the same structure for making migration decisions but vary
based on the metric used to calculate load. For this sequencer workload, the 3
different modes all have the same performance, as shown in
Figure~\ref{fig:mantle-balancer-performance}, because the load balancer falls
into the same mode a majority of the time.  The high variation in performance
for the ``CephFS CPU Mode" bar reflects the uncertainty of using something as
dynamic and unpredictable as CPU utilization to make migration decisions. In
addition to the suboptimal performance and unpredictability, the fact that the
CephFS balancers all fall into the same mode despite using different balancers
is a problem as it prevents administrators from properly exploring the
balancing state space.

Mantle gives the administrator more control over the balancing policies; for
the ``Mantle" bar in Figure~\ref{fig:mantle-balancer-performance} we use the
load balancing interface to program logic for balancing read-heavy workload
into the load balancing service. The resulting performance is more stable and
performs better because we created our own mode for balancing sequencers.

We have identified two balancing modes that are relevant for making migration
decisions for sequencers. Using Mantle, the administrator can put the load
balancing service into ``proxy mode" or ``sequencer mode". In ``proxy mode" one
server receives all requests and farms off the requests to slave servers.  In
``sequencer mode" clients go directly to the server that has their sequencer.
These modes are illustrated in Figure~\ref{fig:mantle-modes}. ``None" is when
all sequencers are co-located on one physical server -- performance for that
mode is shown by the ``No Balancing" curve in
Figure~\ref{fig:mantle-balancer-behaviors}. ``Sequencer" mode in the lower left
shows how clients for sequencer 2 are re-directed to server B. The two ``Proxy"
mode diagrams on the right show how clients continue sending reqeusts to server
A even though sequencer 2 has migrated to server B (the difference between
``Proxy (Half)" and ``Proxy (Full)" is discussed in the next section).

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-mode-behavior.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}]
}\label{fig:mantle-mode-behavior}
\end{figure}

Figure~\ref{fig:mantle-mode-performance} shows the throughput (\(y\) axis) over
time (\(x\) axis) of the two different modes for an environment with only 2
sequencers (again 4 clients each) and 2 servers. The curves for both sequencers
in Figure~\ref{fig:mantle-mode-performance}(a) start at less than 1000
ops/second and at time 60 seconds Mantle migrates Sequencer 1 to the slave
server. Performance of Sequencer 2 decreases because it has stayed on the proxy
which now handles all client requests, processes requests for Sequencer 2, and
forwards requests for Sequencer 1 to the slave server. Sequencer 1 performance
improves dramatically because lookups for that sequencer are parallelized with
the operations on server 1. Cluster throughput improves at the cost of
decreased throughput and unfair throughput shares for Sequencer 2.
Figure~\ref{fig:mantle-mode-performance}(b) is set to sequencer mode manually
(no balancing phase) and shows that performance is worse than proxy mode {\it
and} unfair amongst sequencers. In this case, the scatter-gather process used
for cache coherence in the metadata protocols causes strain on the server
housing Sequencer 2 resulting in uneven performance.

Intuitively, sequencer mode is a superior balancing mode and should perform
better; after all, this is the best strategy for distributing POSIX metadata in
write-heavy workloads~\cite{ren:sc2014-indexfs,
patil:fast2011-giga,sevilla:sc15-mantle}. But our experiments show that proxy
mode is superior for the sequencer's read-heavy workload.  In this case,
separating the handling of the client request and doing the actual operation
improves performance. Processing client requests and doing the actual operation
is too heavy weight for one server and sequencers on slave nodes can go faster
because work is split up; the proxy processes the client request and the slave
finds the tail of the log and delivers the answer.  This phenomenon is not
uncommon and has been observed in chain replication~\cite{CITEME}.

@@

How much load to try and migrate is not a tunable parameter in the original
CephFS balancers. The most useful way to express how much load to send is as a
fraction of some other metric such as total load. Expressing this heuristic is
not easily achievable with outward facing tunable parameters (i.e. system
knobs) but can be expressed with programmability quite easily. To force the
load balancer into ``Proxy (Half)" scenario in Figure~\ref{fig:mantle-modes},
which sets the balancer to proxy mode with migration units of half the load on
the current server we can use the Mantle policy:\\

@@

This code snippet uses globally defined variables and tables from the Mantle
API to send half of the load on the current server (whoami) to the next ranked
server (\#mds + 1); the \texttt{targets} array is a globally defined table that
the balancer uses to do the migrations. Alternatively, to set the mode to the
``Proxy (Full)"` setup in Figure~\ref{fig:mantle-modes}, one would use:\\

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-modes.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}] The
load balancing interface alleviates load for multiple sequencers in
resource-constrained environments.  ``Underloaded (Baseline)'' is the
throughput of one sequencer running alone on a cluster; the other curves show
how load balancing affects the throughput of one sequencer when sequencers for
other logs are initially co-located on the same physical server (i.e. an
"Overloaded" environment).}\label{fig:mantle-modes}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-mode-performance.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}]
}\label{fig:mantle-mode-performance}
\end{figure}

Figure~\ref{fig:mantle-mode-performance} shows the performance of the modes
using different migration units. Recall that this setup only has 2 sequencers
and 2 servers, so performance may be different at scale. Even so, it is clear
sequencer mode does not perform as well for read-heavy workloads and we even
see a throughput improvement when migrating all load off the first server,
leaving the first server to do administrative tasks (this is actually common in
the metadata cluster because the ``first" server does a lot of the cache
coherence work) while the second server does all the client work. Proxy Mode
does the best in both cases and shows large performance gains when completely
decoupling client request handling and operation processing in Proxy Mode
(Full).

The parameter that controls the migration units helps the administrator control
the sequencer or co-location or distribution across the cluster. This trade-off
was explored extensively in the Mantle paper and warrants further exploration
as all our experiments indicate a rich set of states to explore.

\subsubsection{Feature: Backoff Paramters}
\label{sec:feature-backoff}

The balancing phase from 0 to 60 seconds in
Figure~\ref{mantle-balancer-behaviors} shows different degrees of
aggressiveness in making migration decisions; CephFS makes a decision quickly
and throughput jumps 2.5K ops/second within 10 seconds while Mantle takes a
more time to stabilize. This conservative behavior is controlled by programming
the balancer to (1) use different conditions for when to migrate and (2) use a
threshold for sustained overload. \texttt{when()} is part the Mantle API and
the callback expects to return a true or false, which corresponds to whether to
migrate or not. For the Mantle curve in Figure~\ref{mantle-balancer-behaviors}
we set the \texttt{when()} policy to wait for load on the receiving server to
reach 0.1. At the beginning of the run the load of the receiving server spikes
because requests for cache-coherence start as the sequencers are created. It
takes 60 seconds for this load to drop to an acceptable level. Also, the
migration phase is a little more conservative in sending load; the Mantle curve
in Figure~\ref{mantle-balancer-behaviors} takes longer to reach peak throughput
because we do the first migration and {\it wait to see how it affects the
system}; seeing that after migration the third server is still underloaded
allows the balancer to further improve performance by migrating a sequencer to
the laster server.

The other way to change aggressiveness of the decision making is to program
into the balancer a policy that waits a certain number of iterations after a
migration before proceeding. In Mantle, the policy would use the save state
function to do a countdown after a migation:

\begin{figure}[]
\begin{lstlisting}
  countdown = GET_STATE()
  if countdown > 0 then
    -- OK to migrate
  else
    PUT_STATE(countdown - 1)
  end
\end{lstlisting}
\caption{The sequencer balancing policy that works best for bursty workloads. 
\label{listing:greedy-spill}}
\end{figure}

Behavior graphs and performance numbers for this feature is omitted, as the
throughput graphs are as expected: the more conservative the approach the less
overall throughput.

@@

\noindent\textbf{The Malacology Approach:} pull load balancing out of the
storage system to balance sequencers across a cluster. Compared to putting all
sequencers on the same server, load balancing a sequencer per physical server
shows a 1.8\(\times\) throughput improvement.\\

\noindent\textbf{Features:} different load balancing modes control forwarding
vs. client redirection, tuning the backoff parameter controls conservative vs.
aggressive decision making, and tuning load migration unit parameters controls
sequencer distribution vs. co-location.\\

>>>>

We wanted to implement CORFU and we had two choices: build it from the ground
up or do it on top of Malacology. To show the feasability of building on
Malacology our evaluation focuses on the performance of the internal
abstractions used to construct the Mantle and ZLog services. We also discuss
latent capabilities we discovered in this process that lets us navigate
different trade-offs within the services themselves. First, we benchmark
scenarios where contention is at the sequencer by examining the interfaces used
to map ZLog onto Malacology; specifically, we describe the sequencer
implementation and the propagation of object \& data interfaces interfaces.
Next, we benchmark scenarios when there are multiple logs by using Mantle to
balance sequencers across a cluster.

@@

@@

While a best-effort approach to sharing capabilities makes sense for a file
system client, throughput drops significantly with two clients as the majority
of the time neither client has the capability as it ping-pongs between
clients. This observation reveals a tuning parameter: how long a client
maintains its capability lease. In throughput labeled $2C,<time>$ we show
aggregate throughput as we decrease the amount of time that a client holds its
lease before responding to a request for the capability.  At lease times as
low as 10ms throughput achieve a significant proportion of the locally cached
throughput.\\

@@

\subsection{Load Balancing ZLog Sequencers with Mantle}

For scenarios with multiple shared logs and many clients, co-locating
sequencers on the same physical node is not ideal. Unfortunately, building a
load balancer that can migrate the shared resource (in this case, the resource
that mediates access to the tail of the log) would require building subsystems
for migrating resources, monitoring the workloads, collecting metrics that
describe the utilization on the physical nodes, partitioning resources,
maintaining cache coroherence, and managing multiple sequencers.  The following
experiments demonstrate the feasibility of using the mechanisms of the
Malacology load balancing interface to inherit all these features and to
alleviate load from overloaded servers with multiple sequencers.

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-balancer-behaviors.png}
\caption{The load balancing interface lets administrators control the migration
of sequencers in environments with multiple ZLog logs. For this setup (3
sequencers and 3 servers), CephFS and Mantle migrate load and show improved
throughput over the setup where all sequencers are co-located on the same
server (``No Balancing").  Sections~\ref{sec:feature-balancing-modes}
and~\ref{sec:feature-migration-units} quantify the performance improvement of
the stable phase at time 100 seconds and Section~\ref{sec:feature-backoff}
examines the growth phase at time 0 to 60 seconds.
}\label{fig:mantle-balancer-behaviors}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-balancer-performance.png}
\caption{Despite using different balancing modes, the CephFS balancers have the
same performance because they end up migrating the sequencers in the same way.
The Mantle bar programs a balancer designed for sequencers into the service
using the load balancing interface. This is the same workload/setup as
Figure~\ref{fig:mantle-balancer-behaviors}.}\label{fig:mantle-balancer-performance}
\end{figure}

The experiments are run on a cluster with 10 nodes to store objects, one node
to monitor the cluster, and 3 nodes that can accomodate sequencers. Our first
experiment co-locates 3 sequencers each with 4 clients on the same physical
server.  Instead of measuring contention at the clients like
Section~\ref{sec:sequencer-implementation}, these experiments measure
contention at the sequencers by forcing clients to make round-trips every
request. We implement this using the shared resource interface to piggyback on
\texttt{fstat()} and to program a policy into \texttt{getattr()} that forces
round-trips.  Because the sequencer's only function is to  hand out positions
for the tail of the log, the workload is read-heavy.

Figure~\ref{fig:mantle-balancer-behaviors} shows the throughput (\(y\) axis)
over time (\(x\) axis) of different load balancers that migrate ZLog sequencers
acround the cluster; ``No Balancing" keeps all sequencers on one server,
``CephFS" migrates sequencers using the original algorithms packaged with Ceph,
and the ``Mantle" uses a custom load balancer we wrote specifically for
sequencers. The increased throughput for the CephFS and Mantle curves between 0
and 60 seconds are a result of migrating the sequencer(s) off overloadeed
servers. In addition to showing that migrating sequencers improves performance,
Figure~\ref{fig:mantle-balancer-behaviors} also demonstrates features that we
will explore in the rest of this section.
Sections~\ref{sec:feature-balancing-modes}
and~\ref{sec:feature-migration-units} quantify the differences in performance
when the cluster stabilizes at time 100 seconds and
Section~\ref{sec:feature-backoff} examines the slope and start time of the
rebalancing phase between 0 and 60 seconds by comparing the aggressiveness of
the balancers.

@@

The load balancing service can operate in different balancing modes that stress
the subsystems that receive and forward client requests in different ways. In
Figure~\ref{fig:mantle-balancer-behaviors}, the CephFS curve shows the
performance of the balancing mode that CephFS uses {\it most of the time}.
CephFS has 3 modes for balancing load: CPU mode, workload mode, and hybrid
mode. All three have the same structure for making migration decisions but vary
based on the metric used to calculate load. For this sequencer workload, the 3
different modes all have the same performance, as shown in
Figure~\ref{fig:mantle-balancer-performance}, because the load balancer falls
into the same mode a majority of the time.  The high variation in performance
for the CephFS CPU Mode bar reflects the uncertainty of using something as
dynamic and unpredictable as CPU utilization to make migration decisions. In
addition to the suboptimal performance and unpredictability, the fact that the
CephFS balancers all fall into the same mode despite using different balancers
is a problem becuase it prevents administrators from properly exploring the
balancing state space.

Mantle gives the administrator more control over the balancing policies; for
the Mantle bar in Figure~\ref{fig:mantle-balancer-performance} we use the load
balancing interface to program logic for balancing read-heavy workloads,
resulting in higher throughput and better stability.  When we did this we also
identified two balancing modes that are relevant for making migration decisions
for sequencers.

Using Mantle, the administrator can put the load balancing service into ``proxy
mode" or ``client mode". In proxy mode one server receives all requests and
farms off the requests to slave servers; the slaves servers do the actual tail
finding operation. In client mode, clients interact directly with the server
that has their sequencer.  These modes are illustrated in
Figure~\ref{fig:mantle-modes}: ``No balancing" is when all sequencers are
co-located on one physical server -- performance for that mode is shown by the
No Balancing curve in Figure~\ref{fig:mantle-balancer-behaviors}.  ``Client
Mode" in the lower left shows how clients for sequencer 2 are re-directed to
server B. The two ``Proxy mode" diagrams on the right show how clients continue
sending reqeusts to server A even though sequencer 2 has migrated to server B
(the difference between ``Proxy Mode (Half)" and ``Proxy Mode (Full)" is
discussed in the next section).

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-modes.png}
\caption{The client and proxy balancing modes work well for migrating
sequencers to alleviate overloaded servers. Client mode migrates the sequencer
and clients start sending requests to the new server. Proxy mode migrates the
sequencer but clients continue sending their requests to the first server.
``Half"/``Full" indicate the size of the migration units (discussed in
Section~\ref{sec:feature-migration-units}).}\label{fig:mantle-modes}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-mode-behavior.png}
\caption{For this 2 sequencer/2 server setup, the performance of proxy mode
achieves the highest throughput but at the cost of lower throughput for one of
the sequencers. Client mode is more fair but results in lower cluster
throughput; the difference in throughput amongst sequencers can be attributed
to one of the servers doing cache coherence.
}\label{fig:mantle-mode-behavior}
\end{figure}

Figure~\ref{fig:mantle-mode-behavior} shows the throughput (\(y\) axis) over
time (\(x\) axis) of the two different modes for an environment with only 2
sequencers (again 4 clients each) and 2 servers. The curves for both sequencers
in Figure~\ref{fig:mantle-mode-behavior}(a) start at less than 1000 ops/second
and at time 60 seconds Mantle migrates Sequencer 1 to the slave server.
Performance of Sequencer 2 decreases because it stayed on the proxy which now
handles all client requests, processes requests for Sequencer 2, and forwards
requests for Sequencer 1. The performance of Sequencer 1 improves dramatically
because lookups for that sequencer are parallelized with the operations on the
other server. Cluster throughput improves at the cost of decreased throughput
for Sequencer 2.  Figure~\ref{fig:mantle-mode-behavior}(b) is set to sequencer
mode manually (no balancing phase) and shows that the cluster throughput is
worse than the cluster throughput of proxy mode. That graph also shows that
Sequencer 2 has less throughput than Sequencer 2. In this case, the
scatter-gather process used for cache coherence in the metadata protocols
causes strain on the server housing Sequencer 2 resulting in this uneven
performance.

Intuitively, client mode is a superior balancing mode and should perform
better; after all, this is the best strategy for distributing POSIX metadata in
write-heavy workloads~\cite{ren:sc2014-indexfs, patil:fast2011-giga,
sevilla:sc15-mantle}.  But our experiments show that using proxy mode improves
performance for this smale scale setup because it separates (1) the handling of
the client requests and (2) finding the tail of the log and responding to
clients.  Doing both steps is too heavy weight for one server and sequencers on
slave nodes can go faster because work is split up; this phenomenon is not
uncommon and has been observed in chain replication~\cite{CITEME}.

@@

We define a ``migration unit" as the amount of load to try and migrate.  For
example, it is useful to express migration units as a fraction of the total
load.  Expressing this heuristic is not easily achievable with outward facing
tunable parameters (i.e. system knobs) and so the original CephFS balancers do
not have a migration unit tunable.  With programmability, migration units can
be expressed quite easily. To force the load balancer into the Proxy Mode (Half)
scenario in Figure~\ref{fig:mantle-modes}, which sets the balancer to proxy
mode with migration units of half the load on the current server we can use the
Mantle policy:\\

@@

This code snippet uses globally defined variables and tables from the Mantle
API to send half of the load on the current server (whoami) to the next ranked
server (\#mds + 1); the \texttt{targets} array is a globally defined table that
the balancer uses to do the migrations. Alternatively, to set the mode to the
``Proxy (Full)"` setup in Figure~\ref{fig:mantle-modes} we use:\\

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-mode-performance.png}
\caption{The performance of the different modes using various migration units,
indicated by parentheses, shows almost a 2\(\times\) improvement in the best
case.  }\label{fig:mantle-mode-performance}
\end{figure}

Figure~\ref{fig:mantle-mode-performance} shows the performance of the modes
using different migration units. Recall that this setup only has 2 sequencers
and 2 servers, so performance may be different at scale. Even so, it is clear
that client mode does not perform as well for read-heavy workloads. We
even see a throughput improvement when migrating all load off the first server,
leaving the first server to do administrative tasks (this is common in the
metadata cluster because the first server does a lot of the cache coherence
work) while the second server does all the client work. Proxy mode does the
best in both cases and shows large performance gains when completely decoupling
client request handling and operation processing in Proxy Mode (Full).

The parameter that controls the migration units helps the administrator control
the sequencer co-location or distribution across the cluster. This trade-off
was explored extensively in the Mantle paper but the experiments we present
here are indicative of an even richer set of states to explore.

\subsubsection{Feature: Backoff}
\label{sec:feature-backoff}

The balancing phase from 0 to 60 seconds in
Figure~\ref{fig:mantle-balancer-behaviors} shows different degrees of
aggressiveness in making migration decisions; CephFS makes a decision quickly
and throughput jumps to 2500 ops/second within 10 seconds while Mantle takes
more time to stabilize. This conservative behavior is controlled by programming
the balancer to (1) use different conditions for when to migrate and (2) using
a threshold for sustained overload.

We control the conditions for migration using \texttt{when()}. \texttt{when()}
is part the Mantle API and the callback expects a return value of true or
false, which corresponds to whether to migrate or not. For the Mantle curve in
Figure~\ref{fig:mantle-balancer-behaviors} we set the \texttt{when()} policy to
wait for load on the receiving server to fall below a threshold. At the
beginning of the run the load of the receiving server spikes because requests
for cache-coherence start as the sequencers are created. It takes 60 seconds
for this load to drop to an acceptable level and it is at this point that the
migration starts.

The Mantle curve in Figure~\ref{fig:mantle-balancer-behaviors} also takes longer
to reach peak throughput.  This conservative decision making is intentional
because we want the policy wait to see how migrations affect the system before
proceeding. The Mantle curve in Figure~\ref{fig:mantle-balancer-behaviors} does
a migration right before 50 seconds, realizes that there is a third underloaded
server, and does another migration.

The other way to change aggressiveness of the decision making is to program
into the balancer a threshold for sustatined overload. This forces the balancer
to wait a certain number of iterations after a migration before proceeding. In
Mantle, the policy would use the save state function to do a countdown after a
migation.  Behavior graphs and performance numbers for this backoff feature is
omitted for space considerations, but the throughput graphs are as expected:
the more conservative the approach the less overall throughput.\\

@@

\noindent\textbf{The Malacology Approach:} pull load balancing out of the
storage system to balance sequencers across a cluster. Compared to putting all
sequencers on the same server, load balancing a sequencer using proxy mode
shows a 1.8\(\times\) throughput improvement.\\

\noindent\textbf{Features:} different load balancing modes control forwarding
vs. client redirection, tuning the load migration unit parameter controls
sequencer distribution vs. co-location, and tuning the backoff parameter
controls conservative vs.  aggressive decision making.
